\propertitle

### 2019-12-05 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-05T11:13:56+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The conclusions about \enquote{cooperativity} or \enquote{interaction} that
we reach by applying the maximum-entropy method to the larger population,
as proposed here, are therefore different from those applying it at the
sample level -- and also visually clearer. The plot in 
\fig~\ref{fig:plots_2_4mom_a}, showing the two clearly different
distributions constrained by two and four moments, should be compared with
the plot for the distributions obtained at the sample level under the same
constraints, shown in \fig~\ref{fig:comparisons_marginals} as
\textcolor{myred}{red circles} and \textcolor{myblue}{blue squares}. The
measured frequencies (black triangles) are also shown. It is necessary to
use a logarithmic scale to see the differences, which appear mainly in the
tail.
\begin{figure}[!p]
\centering
% \includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
% \\[3em]%
\includegraphics[width=\linewidth]{_scripts/trunct_comparison_marginals.pdf}%
\caption{Marginals for the normalized total activity of the sample,
  obtained from the maximum-entropy distributions with $N=10\,000$ from
  \fig~\ref{fig:plots_2_4mom_a}, and from maximum-entropy distributions
  calculated at the sample level, that is with $N=n=65$.}
\label{fig:comparisons_marginals}
\end{figure}
% comparison_ME_sample_full_levels.nb

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-05T11:17:52+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The conclusions about \enquote{cooperativity} or \enquote{interaction} that
we reach by applying the maximum-entropy method to the larger population,
as proposed here, are therefore different from those applying it at the
sample level -- and also visually clearer. The plot in 
\fig~\ref{fig:plots_2_4mom_a}, showing the two clearly different
distributions constrained by two and four moments, should be compared with
the plot for the distributions obtained at the sample level under the same
constraints, shown in \fig~\ref{fig:comparisons_marginals} as
\textcolor{myred}{red circles} and \textcolor{myblue}{blue squares}. The
measured frequencies (black triangles) are also shown. It is necessary to
use a logarithmic scale to see the differences, which appear mainly in the
tail.
\begin{figure}[!p]
\centering
% \includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
% \\[3em]%
\includegraphics[width=0.95\linewidth]{_scripts/trunct_comparison_marginals.pdf}%
\caption{Marginals for the normalized total activity of the sample,
  obtained from the maximum-entropy distributions with $N=10\,000$ from
  \fig~\ref{fig:plots_2_4mom_a}, and from maximum-entropy distributions
  calculated at the sample level, that is with $N=n=65$, with two and four
  moments in either case.}
\label{fig:comparisons_marginals}
\end{figure}
% comparison_ME_sample_full_levels.nb
